---
title: "Data Scavenger Hunt"
author: "Matthew Davis"
date: "March 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Data Scavenger Hunt.

Rules:  

+ Answers must be results from R code in mark down form:
+ R code must generate the awnsers
+ Output is an html file to upload to oaks via R markdown.
Answers should included the code used to generate.
+ work must be your own by you are encouraged to work in groups

```{r}
library(fivethirtyeight)
data("classic_rock_song_list")
d = as.data.frame(classic_rock_song_list)

```
##### Q1 Which aritist has the song with highest play count for all songs?
```{r}
d[d$playcount == max(d$playcount), 'artist']
```
##### Q2 Which year had the highest average play count?
```{r}
a = aggregate(d$playcount, by=list(d$artist),FUN = sum)
a[a$x == max(a$x),1]
```

##### Q3  Find the artists with the most songs
```{r}
names(table(d$artist)[table(d$artist) == max(table(d$artist))])
```

##### Q4  Find the year the Led Zeppelin released the most songs?
```{r}
s = d[d$artist %in% 'Led Zeppelin','release_year']
names(table(s)[table(s)==max(table(s))])
```

##### Q4 Find the one hit wonder artist with the largest play count for a single song
```{r}
one_hits_aritists = names(table(d$artist)[table(d$artist) ==1 ])
s = d[d$artist %in% one_hits_aritists,]
s[s$playcount == max(s$playcount), 'artist']
```

##### Q5  Find the list of the most repeated song names
```{r}
names(table(d$song)[table(d$song)>2])

```

##### Q6  Of the most repeated song names, figure are they more or less popular that the rest of the group.
```{r}
rep_songs = names(table(d$song)[table(d$song)>1])
rep_song_counts = d[d$song %in% rep_songs, 'playcount']
once_song_counts  = d[!d$song %in% rep_songs, 'playcount']
t.test(rep_song_counts, once_song_counts)
```

##### Q7  find the top three songs in terms of number of plays for the 1990s.
```{r}
s = d[d$release_year %in% 1990:1999,]
tail(s[order(s$playcount), 'song'],3)
```

##### Q8 find the artist with the higest average playcount per year (all years)
```{r}
a = aggregate(d$playcount, by=list(d$artist),FUN = sum)
a[a$x == max(a$x), 1]
```



[]