---
title: "week6_Classic_Rock_Logistic_regresion"
author: "Matthew Davis"
date: "October 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Classic Rock Scavenger Hunt Fall 2018
Answer the following the questions in an R Markdown knitted to html.  Use the play_count variable inside the data set whenever play counts are referenced

```{r, eval=F}
library(fivethirtyeight)
data("classic_rock_song_list")
d = as.data.frame(classic_rock_song_list)
```

#### Plot the denisty of the distrobutions of play counts, with a red vertial line regresenting the play count mean


#### Which aritist has the song with highest play count for all songs?

```{r, eval=F}
d[d$playcount == max(d$playcount), 'artist']
```

####  Which year had the highest average play count?


####   Find the artists with the most songs


#### Create a variable called above_avg inside the data frame

```{r, eval=F}
ifelse(d$playcount > mean(d$playcount) , 1, 0)
d$above_avg = ifelse(d$playcount > mean(d$playcount) , 1, 0)
```

#### what is increase in odds that a song has above average plays if it's by the beatles,  is this a significant increase or decrease? 


#### what is the odds increase for "Rolling Stones", is this a significant increase or decrease? 


#### what artis has the most significant odds increase over getting a song with more than average plays, that also has significant results


#### for every year increase what are the odds of an above average song? Is this a significant result


#### plot the average number of above above average songs per year


#### What does your what can you conclude from your plot and your model about the likely hood of getting a song in the future with above average plays? 


#### Fit a linear regression model using year to total sum number of plays. How many classic rock plays would you expect in 2018?


#### Does this indicate the decline of classic rock ?