---
title: "week10_clustering"
author: "Matthew Davis"
date: "October 29, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


references material
https://www.datascience.com/blog/k-means-clustering



## Custering with kmeans
A  method for finding paterns in unsupervied data ( no outcome labels)

### Objective
to find which countries have similar drinking habbits


#####
* Kmeans start of with randomlly assigned custer centers
* centers are updated at each step using a learning rate and the distance to the mean of their assigned cluster
```{r}
library(fivethirtyeight)
library(ggplot2)
data(drinks)
d = drinks
cols = c('beer_servings', 'spirit_servings') 
d_s = scale(d[, cols])

n_centers = 4

set.seed(2012)
fit<-kmeans(d_s, centers = n_centers, iter.max = i)
d_w_centers = data.frame(d_s)
d_w_centers$cluster = fit$cluster
d_w_centers$type = 'data_points'
d_w_centers$size = 1
centers = data.frame(fit$centers)
centers$cluster = 1:n_centers
centers$type = 'center'
centers$size =3
d_w_centers = rbind(d_w_centers, centers)
  ggplot(d_w_centers, aes(beer_servings,spirit_servings, color=as.factor(cluster)))+ geom_point(aes(shape=type, size=size))
  


```

### Choosing Clusters

```{r}
between = c()
clusters =c()
within = c()
for(i in 2:10){
  fit <-kmeans(d_s, i)
  between = append(between, fit$betweenss)
  within = append(within, fit$tot.withinss)
  clusters = append(clusters, i)
  }
plot(clusters, between, type = 'l')
plot(clusters, within, type = 'l')



````
#### Investigate and Name Clusters


```{r}
d$cluster = as.factor(fit$cluster)
levels(d$cluster) = c('beer drinkin', 'moderate', 'low consuption', 'booze')
print(c(d[d$cluster == 'beer drinkin', 'country']))

```

### Example with Chicago Crime Data
 download the 2018 crime map

https://data.cityofchicago.org/browse?q=crime&sortBy=relevance

```{r load_data}
library(caret)
d = read.csv('data/Crimes_-_Map.csv')
d = na.omit(d)
dmv = caret::dummyVars( ~PRIMARY.DESCRIPTION +  LATITUDE + LONGITUDE + 0, d)
x = predict(dmv, d)
```

```{r}

x_cols = c('PRIMARY.DESCRIPTION','LATITUDE', 'LONGITUDE' )
dmv = caret::dummyVars( ~PRIMARY.DESCRIPTION +  LATITUDE + LONGITUDE + 0, d)
x = predict(dmv, d)

x = x[x[, 'PRIMARY.DESCRIPTION.MOTOR VEHICLE THEFT'] ==1 , ]
x_scaled = scale(x[, x_cols[2:3]])
fit<-kmeans(x_scaled, centers = 4)

predict_kmeans <- function(fit, x){
  n_centers = dim(fit$centers)[1]
  n_rows = dim(x)[1]
  output = matrix(NA, ncol = n_centers, nrow = n_rows)
  for (i in i:n_centers){
   output[,i] = apply(x[, colnames(fit$centers)], 1, FUN=function(x)(sqrt(sum(x, -fit$centers[i,])^2)))
  }
  
  return(output)
  }

p = data.frame(predict_kmeans(fit, x_scaled))
p$centers = apply(p,1, which.min)
p = cbind(x[, x_cols[2:3] ], p)
write.csv(p, 'car_theft.csv')
```

#### Find the worst spot in all of chicago tpo park your car
```{r}
library(fle)
dmv = caret::dummyVars( ~PRIMARY.DESCRIPTION +  LATITUDE + LONGITUDE + 0, d)
x = predict(dmv, d)
cols = c( 'LATITUDE', 'LONGITUDE')
x_train = x[x[, 'PRIMARY.DESCRIPTION.MOTOR VEHICLE THEFT' ] == 1, cols]
fit<-flexclust::kcca(x_train, 10)
new_data= unique(d[, cols])
preds = predict(fit, new_data)


```


